InteroceptionStudy_GPValidation

### 2021-09-01 IAPS_PREPROCESSING_2021_1.Rmd
fix missing pratice in heart rate data of ssid 346-355
The issue was cause dby merging final heart rate with the full dataset using thw wrong tno variable

@@

@@

tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final, by = c('ssid', 'tNo', 'screen_content'))

@@

@@

tmp.df4_sum_full_bio_hr_self <- left_join(tmp.df4_sum_full_bio_hr, db_selfrep, by = 'ssid')

>>>>

table(is.na(db_HR_bio_final$Mean_HR))

@@

unique(tmp.df4_sum_full_bio$screen_content)

@@

db_HR_bio_final

table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))

test<- subset(tmp.df4_sum_full_bio_hr, is.na(Mean_HR))

db_HR_bio_final_norest<- subset(db_HR_bio_final, screen_content!= "Rest")

unique(tmp.df4_sum_full_bio$tNo)

unique(db_HR_bio_final_norest$tNo)

# remeber to do this otherwise tno will be matchjing wrong data
db_HR_bio_final_norest$tNo<- db_HR_bio_final_norest$tNo3

tmp.df4_sum_full_bio_hr <- left_join(tmp.df4_sum_full_bio, db_HR_bio_final_norest, by = c('ssid', 'tNo', 'screen_content'))

@@

table(is.na(tmp.df4_sum_full_bio_hr$Mean_HR))

@@

unique(tmp.df4_sum_full_bio_hr_self$ssid)
table(is.na(tmp.df4_sum_full_bio_hr_self$Mean_HR))
tmp.df4_sum_full_bio_hr_self <- left_join(tmp.df4_sum_full_bio_hr, db_selfrep, by = 'ssid')
